Efficient pedigree recording for fast population genetics simulation

### 2017-11-16 forwards_paper.tex
.

\plr{this paragraph is supposed to cite the fwds time simulation methods we need to}
Forwards-time population genetics simulations are growing in importance,
as the genome-wide impacts of hitchhiking and background selection are more widely appreciated.
For instance, \citet{harris2016genetic} used SLiM \citep{haller2017flexible} to simulate tens of thousands of human exomes
to assess the impact of genetic load and Neanderthal introgression on human genetic diversity.
This is roughly state-of-the-art 
-- the fastest simulation frameworks such as SLiM and fwdpp \citep{fwdpp}
can ``only'' simulate tens of megabases of sequence in tens of thousands of individuals
for tens of thousands of generations --
but still substantially short of whole genomes for most biological population sizes.
There has been some progress at parallelization \citep{lawrie2017accelerating},
which has substantial promise.
The general idea of storing genealogical information to speed up simulations is not new --
it was entirely implemented in AnA-FiTS \citep{aberer2013rapid}, for instance --
but this program did not implement the critical step of discarding irrelevant genealogical information.
A similar but more limited method for discarding this information does appear in \citet{padhukasahasram2008exploring}.

>>>>

\plr{this paragraph is supposed to cite the fwds time simulation methods we need to - @molpopgen fix this up?}
Forwards-time population genetics simulations are growing in importance,
as the genome-wide impacts of hitchhiking and background selection are more widely appreciated.
For instance, \citet{harris2016genetic} used SLiM \citep{haller2017flexible} to simulate tens of thousands of human exomes
to assess the impact of genetic load and Neanderthal introgression on human genetic diversity.
This is roughly state-of-the-art 
-- the fastest simulation frameworks such as SLiM and fwdpp \citep{fwdpp}
can ``only'' simulate tens of megabases of sequence in tens of thousands of individuals
for tens of thousands of generations --
but still substantially short of whole genomes for most biological population sizes.
There has been some progress at parallelization \citep{lawrie2017accelerating},
which has substantial promise.
The general idea of storing genealogical information to speed up simulations is not new --
it was entirely implemented in AnA-FiTS \citep{aberer2013rapid}, for instance --
but this program did not implement the critical step of discarding irrelevant genealogical information.
A similar but more limited method for discarding this information does appear in \citet{padhukasahasram2008exploring}.
